---
title: "Music Through Code"
author: "Anthony Marrero"
date: "2024-11-18"
output: html_document
---
In this R Markdown document I will describe the contents of the dataset and functions involved for my R Programming Final Project.
In the chunk below there will be mock code for what it should look like when the final project is complete.
the first two lines of code will download and setup the Rpackage.
The next two will simply load the data set and provide a summary of it contents
```{r}
#install.package(MusicOde)
#library(MusicOde)
#data(JazzStndrd)
#summary(JazzStndrd)
```
In this next line of code i will introduce the two functions.
The first function will give the original key center and notes for the song. So in the first example the code that should display for the function would be: "Eb Major" and "Eb, F, G, Ab, Bb, C, D"
The second function will give the working chords for the song itself.the code in the second line should display: "Ebmaj7, Edim7, Fm7, F#dim7, etc.."
```{r}
#Scale("It_Could_Happen_To_You")
#Chords("It_Could_Happen_To_You")